\documentclass[a4paper,9.5pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[dvipsnames]{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage[normalem]{ulem}
\pagestyle{empty}

% Section formatting
\titleformat{\section}
  {\color{DarkSlateBlue}\normalfont\bfseries}
  {}
  {0em}
  {\underline}

% Reduce spacing
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=*}
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}

\begin{document}

\begin{center}
    {\Large \textbf{\textcolor{MidnightBlue}{Rafay Adeel}}} \\
    Faisalabad \quad • \quad +92 302 3966541 \quad • \quad \href{mailto:rafayadeel1999@gmail.com}{rafayadeel1999@gmail.com} \\
    \href{https://github.com/CodeRafay}{GitHub} \quad • \quad \href{https://coderafay.github.io/rafay-portfolio/}{Portfolio}
\end{center}

\vspace{-1mm}
\section*{Objective}
Final-year CS student with Python scripting, AI, and cybersecurity experience, seeking a hands-on internship to apply skills in AI systems and secure software development.

\vspace{-1mm}
\section*{Education}
\textbf{BS (Computer Science)}, FAST NUCES — GPA: 3.72

\vspace{-1mm}
\section*{Projects}
\begin{itemize}
    \item \textbf{CForge Compiler (Flex, Bison, LLVM)} – Designed a custom C compiler featuring lexical and syntax analysis, and LLVM-based code generation, demonstrating deep understanding of compiler design and low-level system programming.

    \item \textbf{Mini OS (C++)} – Developed a terminal-based operating system with multitasking, process/thread management, and interrupt handling. Included utilities like a text editor, calculator, and simple games, showcasing OS-level resource control.

    \item \textbf{Chat App (Node.js, JavaScript)} – Built a real-time LAN chat app supporting multi-device messaging over Wi-Fi/LAN, with features like CORS and message logging. Demonstrates network programming and lightweight backend skills.

    \item \textbf{Trie Dictionary (C++)} – Implemented a prefix-based dictionary using Trie data structure supporting efficient add, delete, update, and search operations, highlighting algorithmic optimization and data structure design.

    \item \textbf{Airline Management System (C\#, SQL)} – Created a Windows Forms app managing airline operations such as ticket reservation, flight scheduling, and maintenance tracking, involving database management and user interface design.

    \item \textbf{Transport Management System (C++)} – Developed an OOP-based platform allowing customers to book rides or transport goods with driver acceptance workflow, focusing on object-oriented design and system logic.

    \item \textbf{BINGO Game (C++)} – Developed a two-player console BINGO game that employs arrays, loops, and functions, demonstrating fundamental programming principles and interactive game design.

    \item \textbf{Snake Game (x86 Assembly)} – Programmed a classic Snake game for DOS using x86 Assembly language, enhancing understanding of low-level programming and system interrupts.
\end{itemize}

\vspace{-1mm}
\section*{Skills \& Interests}
\textbf{Languages/Tools:} Python, C, C++, C\#, SQL, JavaScript, HTML/CSS, Oracle, Visual Studio, R, MS Office \\
\textbf{Interests:} Software Development, DevOps, Data Analysis, Project Management

\vspace{-1mm}
\section*{Teaching Assistantships}
\begin{itemize}
    \item PF \quad • \quad OOP \quad • \quad Linear Algebra \quad • \quad Software Design \quad • \quad Database Systems
\end{itemize}

\vspace{-1mm}
\section*{Achievements \& Certifications}
\begin{itemize}
    \item IBM: Python for AI \& Data Science
    \item Google: Cybersecurity, Project Management, Analytics, IT Support
    \item Dean’s List — Fall ’22 to Fall ’24 \quad • \quad Silver Medal — Fall ’22
\end{itemize}

\vspace{-1mm}
\section*{Volunteering \& Leadership}
\begin{itemize}
    \item TEDxFAST Volunteer
    \item Management – Daira \& Job Fair ’23, ’24, ’25
    \item Event Lead — Daira 2025
\end{itemize}

\end{document}
